### 2016-06-18 sec4_baseline.tex
Need to update \eta
Need to describe \eta

\section{Temporal Replication and Mining}
\label{sec:trm}
We resort to the MapReduce (MR) paradigm for designing 
a scalable parallel solution in mining GCMP. It is straightforward 
to partition the trajectory database into equal-sized 
temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
patterns may cross multiple temporal segments. To ensure
the correctness, we need to guarantee that
every valid pattern can be mined within at least 
one partitions.
Thus, some snapshots need to be 
replicated several times in multiple partitions. This
leads us to design the \emph{Temporal Replication and Mining}
(TRM) algorithm.

The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
In brief, there are two pipeline MR jobs which further consist of four stages. 
The first MR job is considered as a preprocessing, where input trajectories
are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
The output is shown as in Figure~\ref{fig:trm}(b). The second
MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
patterns from different partitions are then collected to form the output.

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first MR job which computes the clusters at each snapshot; 
(c)(d) correspond to the second MR job which uses TRM to mine GCMP in parallel.}
\label{fig:trm}
\end{figure*}

Since in the first MR job, each partition contains only one snapshot
for clustering, it is not necessary to replicate any snapshot. Thus, we
focus on describing the second MR job which is the \emph{Temporal
Replication and Mining} algorithm. We use $R$ to denote the replication factor.
The outline of TRM is 
shown in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
We will shortly discuss how the $R$ value is derived. 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $R$ times.
%\subsubsection{Temporal Replication Partition}
The replication factor $R$ is critical for the performance of TRM.
If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $R$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. We will show
later the correctness of this value.

%In the Algorithm~\ref{algo:trm_overview}, 
%the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
%theorem, such a partition method is sound and complete.
%\begin{theorem}[Soundness and Completeness of Replication]
%\label{thm:replication_partition}
%Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
%\end{theorem}
%\begin{proof}
%The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
%Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
%Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
%Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$. This proves the completeness of the partitioning method.
%\end{proof}

\subsection{Line Sweep Mining}
Each task in the reduce phase processes a partition $Par_i$, which contains
$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
only the patterns whose object sets are contained in the first snapshot 
are necessary to be reported. Therefore, we design a simple 
\emph{line-sweep mining}(LSM) method for discovering
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

\begin{algorithm}
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $Par_t = \{S_t, S_{t+1}, ...\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\For{$c \in S_t$} 
\label{code:ls-init-start}
\State $C$.add($\langle c, t \rangle $)
\EndFor
\label{code:ls-init-end}
\ForAll{$i \in [1,R]$}
\State $N \gets S_{t+i} \oplus C$ \label{code:ls-join}
	\ForAll {$n \in N$}
		\If{$|n.O| \geq M$}
			$C$.add($n$).
			\label{code:ls-add}
		\EndIf
	\EndFor
\State{remove unqualified candidate from $C$}
	\label{code:ls-remove}
\EndFor
\State{output qualified candidate in $C$}
\end{algorithmic}
\end{algorithm}

The algorithm scans snapshots in a partition in sequence. During the scan, it
maintains a candidate set $C$ which contains potential patterns (line~\ref{code:ls-can-set}).
The algorithm starts by inserting clusters at $S_i$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
a new set of patterns $N$(lines~\ref{code:ls-join}). The valid new patterns 
form a new candidate set $C$ and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

@@

\subsection{Correctness of TRM}
We prove the correctness of TRM from two aspects. First,
the choice of $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ would 
not miss out any valid patterns. Second, no false patterns
are reported in any partitions. We formalize these two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
\end{definition}

Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We carefully chose $R = (\lceil \frac{K}{L} \rceil -1)*G+2K$ and use
the following theorem to state the correctness:

\begin{theorem}[Correctness of Replication]
\label{thm:replication_partition}
Temporal replication partition is sound and complete.
\end{theorem}z
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. For completeness, with a
valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
with the smallest length. Note that there could be many qualified $T'$s. 
Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
If every partition is of at least such a size, then $T'$ must be
captured by at least one of the partition. Thus, the pattern $P$ would 
be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

%IMPORTANT!!!
%In contrast, it is challenging to design the second job. 
%This is because valid patterns may spray across multiple snapshots 
%or contain different object sets, where inappropriate partitioning
%of snapshots may fail to discover certain valid patterns.
%Formally, a valid partition strategy 
%needs to meet the following requirements: (a) the resulted partitions need
%to preserve enough information so that real patterns can be discovered in the reduce phase. 
%(b) the resulted partitions need to ensure that
%the patterns discovered in the reduce phase are valid patterns so that
%no further verification is required. We formalize these two 
%properties as \emph{completeness} and \emph{soundness} as follows:
%
%\begin{definition}[Completeness and Soundness]
%Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
%\end{definition}
%The completeness ensures that no true patterns are missed out. 
%The soundness ensures that no false patterns are reported. 
%If a partition method is both sound and complete, then it can be used
%in the second MR job to facilitate GCMP mining.
%
%Apparently, replicating the entire trajectories to each 
%partition meets the \emph{soundness} and \emph{completeness} requirements. 
%However, it burdens the network shuffle and limits the parallelism. 
%Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
%In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
%we present a novel \emph{object-based} partition-and-mining method
%called \emph{Star Partition and Mining} (SPM) which resolves
%the deficiencies of TRM method.

>>>>

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two cycles of map-reduce jobs connected in a pipeline manner. The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining. In particular, the timestamp is treated as the key in the map phrase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phrase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of $S_t$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

Our focus in this paper is the second map-reduce cycle of parallel mining, which essentially consists of two key questions to solve. The first is how to employ effective data partitioning such that the mining can be conducted independently; and the second is how to efficiently mine the valid patterns within each partition.

It is obvious that we cannot simply split the trajectory database into disjoint partitions because a GCMP pattern requires $L$-consecutive and the corresponding segments may cross multiple partitions. Our strategy is to use data replication to enable parallel mining. Each snapshot will replicate its clusters to $\eta$ preceding snapshots. In other words, the partition for the snapshot $S_t$ contains clusters in $S_t$, $S_{t+1}\ldots,S_{t+\eta}$. Determining a proper $\eta$ is critical in ensuring the
correctness and efficiency of TRPM. If $\eta$ is too small, certain cross-partition patterns may be missed. If $\eta$ is set too large, expensive network communication and CPU processing costs would be incurred in the map and reduce phrases respectively.

To guarantee that no valid pattern is missing, we enforce the
following statement on $\eta$:
I HAVE NO IDEA WHAT YOU ARE TALKING ABOUT STARTING FROM HERE!!!
 \emph{Let $T'$ be the \emph{shortest} 
valid subsequence (wrt. $K,L,G$) of a valid temporal sequence $T$. 
Then, $\eta$ needs to be the upper bound for all $T'$ among all valid temporal sequences to ensure the completeness.} 
Finding the \emph{minimum} $\eta$ is not
straightforward. We notice the minimum $\eta$ is related to the temporal
parameters $K,L,G$ by making the following observation on $G=1$:

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Mining. (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle which uses temporal replication to mine GCMP in parallel.}
\label{fig:trm}
\end{figure*}

\emph{
Let $T$ be an arbitrary valid temporal sequence. Since $G$ equals to 1,
$T$ can be represented as $T=(t_1, t_2,...,t_m)$, where
$t_i +1 = t_{i+1}$ and $m \geq K$. Let $T' = (t_1,...,t_k)$, $T'$ is the shortest
valid temporal sequence of $T$. Note that $T'$ is fully contained
in the partition $\lambda_{t_1} = \{S_{t_1},...,S_{t_k}\}$, therefore it can be
mined in $\lambda_{t_1}$. 
Since $T$ is an arbitrary valid temporal sequence, the minimum $\eta$ is thus $K$.
}

Inspired by the observation, we generalize the relationship between
the minimum $\eta$ and temporal parameters using the following theorem:

\begin{theorem}
\label{THM:RP_ETA}
The minimum $\eta$ to ensure the completeness of the temporal replication is:
\[
   \eta = 
\begin{cases}
    (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2, & \text{if } G \geq 2\\
    K,              & \text{if } G = 1
\end{cases}
\]
, where $K,L,G$ are the temporal parameters.
\end{theorem}

\begin{proof}
When $G = 1$, we have demonstrated $\eta=K$
in the above observation. When $G \geq 2$, we compute $\eta$ as follows:
any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$.
Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
as follows:
\begin{equation}
\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$; (2)
$\forall g_i, 1 \leq g_i \leq G-1 $; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. Constraints (1)(2)(3) due to the 
validity of $T'$ and $G\geq 2$ (4) is because $|T'|$ is minimum.
Based on (1)(3)(4), we can derive (5):  $n \in [1, \lceil \frac{K}{L} \rceil]$.
Constraints (1)-(5) form a convex polygon and $\eta$ is monotone
increasing wrt. $n, l_i, g_i$, therefore, the maximum value of $\eta$ is taken at the upper boundaries
where $g_i = G-1$, 
$\Sigma_{i=1}^{i=n-1}l_i = K-1$, $l_i = K-1$
and $n = \lceil \frac{K}{L} \rceil$. This leads to  $\eta = (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K -2$.
\end{proof}

Based on the above theorem, during TRPM, every consecutive $\eta$ snapshots
form a partition. In particular, for every snapshot $S_t$, there is
a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. With this partition strategy,
when discovering GCMPS in $\lambda_t$, we only need to keep the pattern candidates whose
object set are in $S_t$. This motivates to design an efficient 
\emph{line-sweep} mining (LSM) method for each partition. The intuition of LSM is 
to sequentially scan all snapshots. During scanning, a set of pattern candidates is maintained.
When all snapshots are scanned, the remaining candidates are the true patterns.
The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
false patterns are deleted (line~\ref{code:ls-remove}). 
Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.

\begin{algorithm}
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\For{$c \in S_t$} 
\label{code:ls-init-start}
\State $C$.add($\langle c, t \rangle $)
\EndFor
\label{code:ls-init-end}
\ForAll{$j \in [t+1,t+\eta-1]$}
\State $C \gets S_{j} \oplus C$ \label{code:ls-join}
	\State{remove false candidates from $C$}
	\label{code:ls-remove}
\EndFor
\State{output true candidates in $C$}
\end{algorithmic}
\end{algorithm}

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
during sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns whose object set is in snapshot $S_1$.
As line sweeps, the patterns in $C_i$ grows. At snapshot $S_4$, the candidate
$\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$ constraint.
Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
because its local consecutive timestamps $\{4\}$ has only size $1$,
which violates the $L$ constraint.
Finally, $\{o_3,o_4\}$ is the qualified pattern and is outputted. Note that the minimum $\eta$
under this setting is $5$. If $\eta$ is chosen as $4$, the pattern $\{o_3,o_4\}$ would be excluded.

\begin{algorithm}
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit a $\langle \max(t-i,0), S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, \lambda_t\rangle$
\State where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,\lambda_t \rangle$}
\State lineSweepMining($\lambda_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

### 2016-06-18 sec5_spm.tex
Need to update \eta
Need to describe \eta

\section{Star Partition and Mining}
\label{sec:spm}
TRM approach requires to replicate entire
trajectories $O(|\mathbb{T}|)$ times, which is inefficient
in parallelism. To overcome this limitation, we 
propose the \emph{Star Partition and Mining} (SPM) method.
In SPM, we design a graph model, named \emph{connection graph}, to capture 
the co-moving behavior among objects. In such a way, 
given an object $u$, all the objects potentially
co-moved with $u$ are captured in $u$'s neighborhood, which
forms a \emph{star} structure in graph terms. SPM utilizes
such structures to partition objects and then adapts an Apriori 
algorithm to discover true GCMPs from each partition.

@@

It is notable that, in star partition, original data is 
replicated for $O(|\mathbb{O}|)$ times as each object may 
be sent to $O(|\mathbb{O}|)$ stars. Since in reality, $|\mathbb{T}| \gg |\mathbb{O}|$, 
the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
%It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
%time to mine GCMP. There are two major factors dragging 
%down the performance. First, the size of $Sr_s$ affects the initial 
%size of $2$-patterns. Second, the candidates generated in each 
%level affects the join performance. In later
%sections, we exploit some properties of GCMP to reduce the two factors.

@@

\subsubsection{Correctness}
Although star partition is performed based on the connection graph, 
each star is indeed a projection of original trajectories.
To see this, each vertex can be viewed as an object. 
The timestamps of center vertex $s$ is the union of all the 
edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
edge $e(s,v)$. Therefore, stars can be viewed as a trajectory
database, where GCMP can be similarly defined. Using the same 
notions as Definition 4, we state the correctness
of star partition as follows:

\begin{theorem}[Soundness and Completeness of Star Partition]
Star partition is sound and complete.
\end{theorem}

\begin{proof}
For the soundness,
if $P$ is a valid pattern in $Sr_s$, then at every time $t$, 
$\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
By definition, $P$ is valid in the original trajectories.
For the completeness,
if $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
\end{proof}

@@

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For an random numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
Let $d_i$ denote the degree of vertex $i$ in $G$. 
It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the vertex
with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) 
						&\leq \exp(\frac{-2t^2}{n}) \\
						&= \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

>>>>

\section{Star Partition and Mining}
\label{sec:spm}
To resolve the two limitations of TRM, we 
propose the \emph{Star Partition and Mining} (SPM) method.
Instead of partition trajectory database in the temporal domain,
SPM partition the trajectory database in the object domain.
Specifically, we design a graph model, named \emph{connection graph}, to capture 
the co-moving behavior among objects. In such a way, 
given an object $u$, all the objects potentially
co-moved with $u$ are captured in $u$'s neighborhood, which
forms a \emph{star} structure in graph terms. SPM utilizes
such structures to partition objects and then adapts an Apriori 
algorithm to discover true GCMPs from each partition.

@@

It is notable that, in star partition, original data is 
replicated at most $O(|\mathbb{O}|)$ times.
In later sections, we will describe several 
more optimization techniques to further reduce the amount of replicated data.
%It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
%time to mine GCMP. There are two major factors dragging 
%down the performance. First, the size of $Sr_s$ affects the initial 
%size of $2$-patterns. Second, the candidates generated in each 
%level affects the join performance. In later
%sections, we exploit some properties of GCMP to reduce the two factors.

@@

\subsubsection{Correctness}
An important concern in star partition is that
whether any valid patterns are missed out by 
such a partition. We assert the correctness by 
the following theorem:
\begin{theorem}[Correctness of Star Partition]
\label{THM:SPM_CORRECT}
Star partition is complete.
\end{theorem}

In fact, besides that every valid patterns can be
mined in some stars, star partition further ensures
that patterns discovered
from different star partitions cannot be the same. 
This can be formulated as:

\begin{lemma}[Unique Patterns in Star Partition]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two stars. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $P_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j, p_i.O \not\equiv p_j.O$.
\end{lemma}

This lemma indicates that every star partition discovers different patterns,
thus less redundant work could exist as opposed to the line sweep method in TRM.

@@

\begin{theorem}[Balance of Star Partition]
\label{THM:SPM_LB}
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For an random numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is with probability $1-1/n$, 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

### 2016-06-18 sec6_optimization.tex
Need to update \eta
Need to describe \eta

\begin{theorem}[Temporal Monotonicity]
Given the temporal parameters $L,G,K$, for a candidate pattern $P$,
if $P.T$ cannot be simplified to a candidate sequence,
then, for any candidate $P'$ with $P.O \subseteq P'.O$, $P'$ cannot be a true pattern.
\end{theorem}
\begin{proof}
Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
by proof of contradiction, any subset of $P_1.T$ cannot
be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
\end{proof}

@@

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking]
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

\begin{proof}
We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
\end{proof}

>>>>

\begin{theorem}[Temporal Monotonicity]
\label{THM:SPM_TM}
Given the temporal parameters $L,G,K$, for a candidate pattern $P$,
if $P.T$ cannot be simplified to a candidate sequence,
then, for any candidate $P'$ with $P.O \subseteq P'.O$, $P'$ cannot be a true pattern.
\end{theorem}

@@

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking]
\label{THM:SPM_FCC}
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}
